Refinement for open automata

### 2021-06-23 2021-Refinement/report.tex
Minor corrections

	For the left side we use the preservation of reachability across transitions:

@@

	For the right side we use the preservation of reachability across transitions:

@@

Let \(v_3 \mapsto v_{3x}\) is the renaming for \(v_3 \in V_3\) in \(A_{x3}\).

@@

	For the middle part we use the preservation of reachability across transitions:

@@

Let \(v_1 \mapsto v_{1x}\) is the renaming for \(v_1 \in V_1\) in \(A_{x1}\).

>>>>

	For the left side we use the definition of reachability (reachability is preserved across transitions):

@@

	For the right side we use the definition of reachability (reachability is preserved across transitions):

@@

Let \(v_3 \mapsto v_{3x}\) be the renaming for \(v_3 \in V_3\) in \(A_{x3}\).

@@

	For the middle part we use the definition of reachability (reachability is preserved across transitions):

@@

Let \(v_1 \mapsto v_{1x}\) be the renaming for \(v_1 \in V_1\) in \(A_{x1}\).
